Supplemental Materials

### 2021-05-27 supplement/supplement-main.Rmd
supp demo table created

---
title: "Supplemental Materials"
subtitle: "Untitled vaccination intuitive theory paper"
authors: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document: 
    latex_engine: xelatex
    fig_caption: yes
figsintext : yes
always_allow_html: true
header-includes:
 \usepackage{float}
---

@@

```{r, echo=F, message=F, warning=F, fig.width=4, fig.height=3, fig.align='center', fig.cap="Example DAG representing some variables related to wildfires"}

@@

	  # Graph
	  graph [overlap = true, fontsize = 8]
	}"
) %>%
  export_svg() %>%
  xml2::read_xml() %>%
  xml2::write_xml("../local/graph.svg")

knitr::include_graphics("../local/graph.svg")
```

@@

$$y = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$

@@

```{r cross_validation, echo=FALSE, fig.height=4, fig.width=6, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}

@@

cv_res %>% 
  ggplot(aes(x=reorder(algo, loss), y=loss)) +
  geom_boxplot() +
  coord_flip() +
  labs(y = "Log-likelihood loss", x = "Algorithm")

@@

# this is the favorite son (most likely)
main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
plot(h)
```

@@

# set.seed(49126)
# 
# train_noise <- train %>%
#   mutate_all(~.x+rnorm(n(),0,.002))
# 
# cl = parallel::makeCluster(detectCores(logical=TRUE))
# 
# clusterCall(cl,
#             function(){
#               source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
#               library(purrr)
#               }
#   )
# 
# ## very slow!
# boot_res <- boot.strength(
#   train_noise,  #train
#   R = 200,
#   algorithm = "hc",
#   algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
#   cluster = cl
#   )
# 
# stopCluster(cl)
# 
# saveRDS(boot_res,"../local/boot_res.rds")

# this runs for hours and hits an error on optim(), 
# possibly a bootstrap replicate was not full rank / produced huge colinearity?
# possibly getting a perfect prediction and coef --> infinity for some variable?
# maybe adding a tiny bit of noise would help?
```

@@

```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1."}

@@

model_fits <- tibble(
  varName = as.character(colnames(d_bn)),
  # model_fit = c(.50, .66, .48, .63, .64, .56, .71, .35, .63, .90, .83, .86, .81, .87),
  `test-retest` = test_retest$fit,
  `maximal` = oos_fits$fit
  ) %>%
  mutate(varName = recode_nodes(varName)) %>% 
  left_join(corrDF, by ="varName") %>% 
  rename(`Bayesian network` = cor) %>% 
  gather(model, fit, `Bayesian network`, `test-retest`, `maximal`) %>%
  mutate(n = ifelse(model=="test_retest", 233, 226)) %>%
  mutate(ul = r_upper(fit,n), ll= r_lower(fit,n))

@@

```{r, echo=FALSE, message=F, fig.height=8, fig.width=8, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1. Correlation matrix is arranged by hierarhical clustering algorithm to highlight connections among beliefs."}
# plot correlation matrix
library(corrplot)

@@

ggplot(temp_cor_df,
       aes(x = reorder(scale1, desc(order1)), 
           y = reorder(scale2, order2), 
           fill = cor)) +
  geom_tile(color = "black") +
  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3.5) +
  scale_fill_distiller(palette ="RdBu", limits = c(-1, 1),
                     guide = guide_colorbar(barheight = 15)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title = element_blank(),
        aspect.ratio=1) +
  labs(fill = "Corr.")
```

@@

[table will go here]

```{r, include=FALSE}
# compute overall demographics for all studies for paper
s1_demo <- s1_all %>% 
  filter(exclude==0) %>% 
  select(workerId, age, sex, race, religion, educ, income, parent)

# s2_demo needs recoding / renaming
# s3_demo good 
# s4_demo same as s1

# and create big table with table1 and t1kable()
```

>>>>

---
title: "Supplemental Materials"
subtitle: "Untitled vaccination intuitive theory paper"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document: 
    latex_engine: xelatex
    fig_caption: yes
figsintext : yes
always_allow_html: true
header-includes:
 \usepackage{float}
---

@@

```{r dag_example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfiles."}

@@

	  # Graph
	  graph [overlap = true, fontsize = 8]
	}"
)
```

@@

$$P(y) = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$

@@

```{r cross_validation, echo=FALSE, fig.align='center', fig.height=3, fig.width=4, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}

@@

cv_res %>% 
  ggplot(aes(x=reorder(algo, loss), y=loss)) +
  geom_boxplot(fill="skyblue") +
  coord_flip() +
  labs(y = "Log-likelihood loss", x = "Algorithm") +
  theme_bw() +
  theme(panel.grid = element_blank())

@@

# this is the favorite son (most likely)
main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))

```{r main_model_plot, echo=F, fig.align='center', fig.width=7, fig.height=7, fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions."}
plot(h)
```

@@

set.seed(49126)

# train_noise <- train %>%
#   mutate_all(~.x+rnorm(n(),0,.002))

cl = parallel::makeCluster(detectCores(logical=TRUE))

clusterCall(cl,
            function(){
              source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
              library(purrr)
              }
  )

## very slow!
boot_res <- boot.strength(
  train,  #train
  R = 50,
  algorithm = "hc",
  algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
  cluster = cl
  )

stopCluster(cl)

saveRDS(boot_res,"../local/boot_res.rds")

# this runs for hours and hits an error on optim(), 
# possibly a bootstrap replicate was not full rank / produced huge collinearity?
# possibly getting a perfect prediction and coef --> infinity for some variable?
# maybe adding a tiny bit of noise would help?
```

@@

```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1. Dashed lines represent perfect fits."}

@@

model_fits <- tibble(
  varName = as.character(colnames(d_bn)),
  `test-retest` = test_retest$fit,
  `maximal` = oos_fits$fit
  ) %>%
  mutate(varName = recode_nodes(varName)) %>% 
  left_join(corrDF, by ="varName") %>% 
  rename(`Bayesian network` = cor) %>% 
  gather(model, fit, `Bayesian network`, `test-retest`, `maximal`) %>%
  mutate(n = ifelse(model=="test_retest", 233, 226)) %>%
  mutate(ul = r_upper(fit,n), ll= r_lower(fit,n))

@@

```{r, echo=FALSE, message=F, fig.height=7, fig.width=7, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1. Correlation matrix is arranged by hierarhical clustering algorithm to highlight connections among beliefs."}
# plot correlation matrix
library(corrplot)

@@

ggplot(temp_cor_df,
       aes(x = reorder(scale1, desc(order1)), 
           y = reorder(scale2, order2), 
           fill = cor)) +
  geom_tile(color = "black") +
  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3) +
  scale_fill_distiller(palette ="RdBu", limits = c(-1, 1),
                     guide = guide_colorbar(barheight = 15)) +
  theme_minimal(base_size=12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title = element_blank(),
        aspect.ratio=1) +
  labs(fill = "Corr.")
```

@@

The table below presents demographic information for participants across all four studies.

```{r, include=FALSE}
library(table1)

# compute overall demographics for all studies for paper
s1_demo <- s1_all %>% 
  filter(exclude==0) %>% 
  mutate(age = as.numeric(age)) %>% 
  select(workerId, age, sex, race, religion, educ, income, parent) %>% 
  mutate(study = "1") %>% 
  mutate(
    # educ = gsub(" or Professional Degree", "Degree", educ),
    educ = gsub(" or Professional","", educ),
    educ = gsub(" Education","", educ),
    educ = gsub(" or Equivalent", "", educ),
    educ = ifelse(grepl("Click to", educ),NA,educ),
    income = gsub("30,0000","30,000", income),
    religion = gsub(",","", religion),
    parent = ifelse(parent=="", NA, parent)
  )

df_demo <- s1_demo %>% 
  bind_rows(
    s2_demo %>% 
      select(workerId, age, sex, race, religion, educ, income, parent) %>% 
      mutate(
        study = "2",
        )
  ) %>% 
  bind_rows(
    s3_demo %>% 
      mutate(
        study = paste0("3",study),
        sex = ifelse(sex=="female","Female","Male")
        ) %>% 
      select(workerId, age, sex, race, religion, educ, income, parent, study)
  ) %>% 
  bind_rows(
    s1_demo %>% 
      filter(workerId %in% s4_wide$workerId) %>% 
      mutate(study = "4")
  ) %>% 
  mutate(
    race = ordered(race,
                   levels = c(
                          "White",
                          "Black or African American",
                          "Hispanic/Latino",
                          "Hawaiian or PI",
                          "Asian",
                          "Native American",
                          "Other or prefer not to say"
                          )
                   ),
    educ = ordered(educ,
                   levels = c(
                          "No Diploma",
                          "High School",
                          "Some Undergraduate",
                          "Undergraduate Degree",
                          "Some Graduate",
                          "Graduate Degree",
                          "Doctorate",
                          "Prefer not to say"
                          )
                   ),
    income = ordered(income,
                     levels = c(
                          "Less than $20,000",
                          "$20,000 - $30,000",
                          "$30,001 - $50,000",
                          "$50,001 - $70,000",
                          "$70,001 - $100,000",
                          "More than $100,000",
                          "Prefer not to say"
                          )
                     )

  ) %>% 
  mutate(
    age = ifelse(age < 18,NA,age),
    income = str_replace_all(income, "\\$",""),
    study = paste("Study", study)
    )

label(df_demo$sex) <- "Gender"
label(df_demo$age) <- "Age"
label(df_demo$race) <- "Race"
label(df_demo$religion) <- "Religion"
label(df_demo$educ) <- "Education"
label(df_demo$income) <- "Income ($)"
label(df_demo$parent) <- "Parent?"

# and create big table with table1 and t1kable()
demographics_tbl <- table1::table1(~ sex + age + race + religion + educ + income + parent  | study, data=df_demo)

table1::t1kable(demographics_tbl, full_width=F) %>% 
  kable_classic()
